%!TEX root=cs112S2014-lab8.tex 
% mainfile: cs112S2014-lab8.tex 

\input{labspre.tex}

\usepackage[compact]{titlesec}

\begin{document} \MYTITLE{Laboratory Assignment Eight: Queue-Based Simulation of the Josephus Problem}
\MYHEADERS{Laboratory Assignment Eight}{Due: April 15, 2014}

\section*{Introduction}

  Many real-world programs use the queue abstract data type (ADT) to solve a problem.  For instance, an operating system
  may use a round-robin scheduler that leverages a queue to determine which process it should execute next. In this
  laboratory assignment, you will use a linked-list-based queue, called the {\tt NodeQueue}, to run a ``simulator'' that
  can solve the Josephus problem. Then, you will analyze the source-code of the simulator to determine its worst-case
  time complexity and then  

\section*{Learning About the Queue}

  Before you start to extend the implementation of the provided {\tt JosephusSolver}, you should take some time to learn
  more about the queue ADT.  What are the methods that the queue provides?  What is the difference between an {\tt
    ArrayQueue} and a {\tt NodeQueue}? What is an example of a problem that can be solved using the queue? Your response
  to this question should include a brief introduction to the problem and a discussion of how the queue is incorporated
  into the solution. For instance, you could explain a program that you have already implemented that manipulated a
  queue to solve a problem.  Alternatively, you can study books, articles, and online sources to investigate a
  well-known problem that can be solved through the use of a queue.  Please see the instructor if you have questions
  about this part of the assignment.

\section*{Using Simulation to Solve the Josephus Problem}

  Many children have played the game of ``hot potato'' that requires them to sit in a circle and pass an object around
  the circle until a leader rings a bell or stops playing some music.  At this point in the game, the child holding the
  potato must stop playing the game and, after the remaining children move closer together in the circle, the game
  continues in the same fashion. This game play continues until there is only one child left, who is then declared the
  winner.

  It turns out that this game was first recorded by Flavius Josephus, a first century Jewish historian who was a solider
  in a Jewish-Roman war.  It is possible to use a queue to ``simulate'' the process of playing this game and then
  quickly determine who will win.  \mbox{After typing} the command {\tt git pull} in the {\tt cs112S2014-share}
  repository, you will see that there is \mbox{now a} {\tt labs/lab8/} directory that contains a {\tt build.xml} file, a
  {\tt net-datastructures-5-0.jar} Java archive, and {\tt JosephusSolver.java} file in the {\tt
    src/edu/allegheny/solver/} directory.  You can run this program by typing {\tt ant JosephusSolver} in the terminal
  or {\tt :Ant JosephusSolver} \mbox{in GVim}.

  If you study {\tt JosephusSolver.java} you will notice that it contains a {\tt main} method that creates different
  groups of children and then runs the solver by specifying a group of children and a stopping point for each round.
  While this approach is suitable for demonstrating the use of the solver, it is not ideal if you need to run a series
  of experiments to evaluate the efficiency of this technique. Therefore, you should modify the program so that it
  accepts two command-line arguments: the number of children involved in the simulated game and the number of steps for
  which each round must be run. Next, you should enhance the program so that it

\section*{Evaluating the Efficiency of the Solver}

\section*{Summary of the Required Deliverables}

  This assignment invites you to submit a signed and printed version of the following deliverables: 

  \begin{enumerate} 
  \itemsep0pt

  \item A complete description of a problem that can be solved by using the queue abstract data type

  \item The properly commented version of {\tt JosephusSolver.java} and any other Java files you create

  \item The output from five separate runs of {\tt JosephusSolver}, demonstrating it's correctness 

  \item A written report that provides a response to all of the questions posed in this assignment

  \item A written analysis of the {\tt JosephusSolver}'s efficiency when it is run in different configurations 

  \item A reflective commentary on the challenges that you faced when completing this assignment 
   
  \end{enumerate}

  Along with turning in a printed version of these deliverables, you should ensure that everything is also available in
  the repository that is named according to the convention {\tt cs112S2014-<your user name>}. Please note that students
  in the class are responsible for completing and submitting their own version of this assignment.    While it is
  acceptable for members of this class to have high-level conversations, you should not share source code or full
  command lines with your classmates.  Deliverables that are nearly identical to the work of others will be taken as
  evidence of violating the \mbox{Honor Code}.  Please see the instructor if you have questions about the policies for
  this assignment.

  \end{document}
